Application for Rethinking Foundations of Physics 2017

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
"Rethinking Foundations of Physics 2017\application.tex" Fix biblatex path error?
Updates from ShareLaTeX
"Rethinking Foundations of Physics 2017\application.lyx" It seems its LyX bug... Will send LyX ticket later...
application.tex \section{Statement of Motivation} Modified accordingly...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
%\addbibresource{../proposal/prop.bib}
%%\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
%% \addbibresource{"../proposal/prop.bib"}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}

@@

Physical processes are ultimately bounded in space, time, energy, and
other resources. Yet, for centuries, the mathematical formalization of
such processes has been founded on the infinitely precise real or
complex numbers. Indeed, physics textbooks casually refer to entities
such as $e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective,
such numbers do not exist in their entirety ``for free.''  For
example, the state of the art algorithms for computing the $n$th
binary digit of~$\pi$ require on the order of $O(n\log^{O(1)}(n))$
operations~\cite{journals/moc/BaileyBP97}. In other words, simply
referring to the $n$th digit of $\pi$ requires more and more resources
as $n$ gets larger. Taking such resource bounds into consideration is
what founded computer science as a discipline and is crucial for
understanding the very nature of computation and, following
Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.

@@

\begin{comment}
\bibliographystyle{plain}
\bibliography{prop}
\end{comment}
\printbibliography 
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
\addbibresource{../proposal/prop.bib}
\addbibresource{cites1.bib}
%%\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
%%\addbibresource{"../proposal/prop.bib"}
%%\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}

@@

Physical processes are ultimately bounded in space, time, energy,
and other resources. Yet, for centuries, the mathematical formalization
of such processes has been founded on the infinitely precise real
or complex numbers. Indeed, physics textbooks casually refer to entities
such as $\rme$, $\pi$, $\sqrt{2}$, etc~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
From a computational perspective, such numbers do not exist in their
entirety ``for free.'' For example, the state of the art algorithms
for computing the $n$th binary digit of~$\pi$ require on the order
of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$ operations~\cite{journals/moc/BaileyBP97}.
In other words, simply referring to the $n$th digit of $\pi$ requires
more and more resources as $n$ gets larger. Taking such resource
bounds into consideration is what founded computer science as a discipline
and is crucial for understanding the very nature of computation and,
following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.

@@

\begin{comment}
\bibliographystyle{plain}
\bibliography{../proposal/prop.bib}
\bibliography{cites1.bib}
\end{comment}
\printbibliography 
\end{document}
